Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-06-15 PAPER.tex
edit to fig 6 caption

Our numerical test reveals that the convergence rates of empirical eigenvectors is related to the sample variance in our empirical estimate. In general, computing an empirical covariance from a finite ensemble average means that the empirical eigenmodes have sample variances. Consider first a limiting case where all eigenvalues are equal. In such a scenario, any linear combination of eigenvectors is also an eigenvector, and thus there is no sensible way to define the convergence of eigenvectors. In our current test, aside from the first mode, the eigenvalues have similar values but are not precisely equal. There are thus a well-defined set of eigenvectors to converge to. However, due to the sample variance of our empirical covariance estimate, there may be accidental degeneracies between modes, where some modes are mixing and swapping with others. Therefore, the steeper an eigenspectrum, the easier it is for the eigenmodes to de-couple from each other and approach their true forms. A particularly drastic example of this can be seen in the behavior of mode $0$ (the foreground mode), whose eigenvalue differs enough from the others that it is able to converge reasonably quickly despite substantial sample variance in our empirical covariance estimate. To break degeneracies in the remaining modes, however, requires many more realizations.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{plots/toy_sigloss17.pdf}
	\caption{The convergence level, as defined in Equation \eqref{eq:converge_eig}, of empirically estimated eigenvectors for different numbers of mock data realizations. The colors span from the 0th eigenmode (has the highest eigenvalue) to the 19th eigenmode (has the lowest eigenvalue), where they are ordered by eigenvalue in descending order. This figure shows that the 0th eigenmode converges the quickest, implying that eigenvectors that differ in structure from those of the EoR (i.e. the FG-dominated mode in the toy model has a different covariance structure than the EoR) converge to the true eigenvectors the quickest.}
	\label{fig:toy_sigloss17}
\end{figure}

>>>>

Our numerical test reveals that the convergence rates of empirical eigenvectors is related to the sample variance in our empirical estimate. In general, computing an empirical covariance from a finite ensemble average means that the empirical eigenmodes have sample variances. Consider first a limiting case where all eigenvalues are equal. In such a scenario, any linear combination of eigenvectors is also an eigenvector, and thus there is no sensible way to define the convergence of eigenvectors. In our current test, aside from the zeroth mode, the eigenvalues have similar values but are not precisely equal. Hence, there is a well-defined set of eigenvectors to converge to. However, due to the sample variance of our empirical covariance estimate, there may be accidental degeneracies between modes, where some modes are mixing and swapping with others. Therefore, the steeper an eigenspectrum, the easier it is for the eigenmodes to de-couple from each other and approach their true forms. A particularly drastic example of this can be seen in the behavior of mode $0$ (the foreground mode), whose eigenvalue differs enough from the others that it is able to converge reasonably quickly despite substantial sample variance in our empirical covariance estimate. To break degeneracies in the remaining modes, however, requires many more realizations.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{plots/toy_sigloss17.pdf}
	\caption{The convergence level, as defined in Equation \eqref{eq:converge_eig}, of empirically estimated eigenvectors for different numbers of mock data realizations. The colors span from the 0th eigenmode (has the highest eigenvalue) to the 19th eigenmode (has the lowest eigenvalue), where they are ordered by eigenvalue in descending order. This figure shows that the 0th eigenmode converges the quickest, implying that eigenvectors with eigenvalues that are substantially different than the rest (i.e. the FG-dominated mode has a much higher eigenvalue than the EoR modes) are able to converge to the true eigenvectors the quickest. On the other hand, eigenmodes $1$-$19$ have similar eigenvalues and are slower to converge because of degeneracies between them.}
	\label{fig:toy_sigloss17}
\end{figure}
